Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
reloading darios comments

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem. Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual domain of the controller, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser which is used to try and synthesise a real plant. In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis. \textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.
}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
The benchmarks used are from existing work on verification. There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons. 
}
\end{quote}
